---
title: "Phoenix Suns Heatmaps"
author: "Andrew Lujan"
date: '2022-06-07'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load Basketball Packages

```{r}
library(ggplot2)
library(tidyverse)
library(nbastatR)
library(devtools)
library(ncaahoopR)
library(extrafont)
library(cowplot)
library(gridExtra)

```

## Create The court

```{r}

# Creating court and plotting
circle_points = function(center = c(0, 0), radius = 1, npoints = 360) {
  angles = seq(0, 2 * pi, length.out = npoints)
  return(data_frame(x = center[1] + radius * cos(angles),
                    y = center[2] + radius * sin(angles)))
}
# Court Dimenons & lines
width = 50
height = 94 / 2
key_height = 19
inner_key_width = 12
outer_key_width = 16
backboard_width = 6
backboard_offset = 4
neck_length = 0.5
hoop_radius = 0.75
hoop_center_y = backboard_offset + neck_length + hoop_radius
three_point_radius = 23.75
three_point_side_radius = 22
three_point_side_height = 14
# Court themes
court_themes = list(
  light = list(
    court = 'floralwhite',
    lines = '#999999',
    text = '#222222',
    made = '#00bfc4',
    missed = '#f8766d',
    hex_border_size = 1,
    hex_border_color = "#000000"
  ),
  dark = list(
    court = '#000004',
    lines = '#999999',
    text = '#f0f0f0',
    made = '#00bfc4',
    missed = '#f8766d',
    hex_border_size = 0,
    hex_border_color = "#000000"
  ),
  ppt = list(
    court = 'gray15',
    lines = 'white',
    text = '#f0f0f0',
    made = '#00bfc4',
    missed = '#f8766d',
    hex_border_size = 0,
    hex_border_color = "gray15"
)
)
# Function to create court based on given dimensions
plot_court = function(court_theme = court_themes$light, use_short_three = FALSE) {
  if (use_short_three) {
    three_point_radius = 22
    three_point_side_height = 0
  }
  
  court_points = data_frame(
    x = c(width / 2, width / 2, -width / 2, -width / 2, width / 2),
    y = c(height, 0, 0, height, height),
    desc = "perimeter"
  )
  
  court_points = bind_rows(court_points , data_frame(
    x = c(outer_key_width / 2, outer_key_width / 2, -outer_key_width / 2, -outer_key_width / 2),
    y = c(0, key_height, key_height, 0),
    desc = "outer_key"
  ))
  
  court_points = bind_rows(court_points , data_frame(
    x = c(-backboard_width / 2, backboard_width / 2),
    y = c(backboard_offset, backboard_offset),
    desc = "backboard"
  ))
  
  court_points = bind_rows(court_points , data_frame(
    x = c(0, 0), y = c(backboard_offset, backboard_offset + neck_length), desc = "neck"
  ))
  
  foul_circle = circle_points(center = c(0, key_height), radius = inner_key_width / 2)
  
  foul_circle_top = filter(foul_circle, y > key_height) %>%
    mutate(desc = "foul_circle_top")
  
  foul_circle_bottom = filter(foul_circle, y < key_height) %>%
    mutate(
      angle = atan((y - key_height) / x) * 180 / pi,
      angle_group = floor((angle - 5.625) / 11.25),
      desc = paste0("foul_circle_bottom_", angle_group)
    ) %>%
    filter(angle_group %% 2 == 0) %>%
    select(x, y, desc)
  
  hoop = circle_points(center = c(0, hoop_center_y), radius = hoop_radius) %>%
    mutate(desc = "hoop")
  
  restricted = circle_points(center = c(0, hoop_center_y), radius = 4) %>%
    filter(y >= hoop_center_y) %>%
    mutate(desc = "restricted")
  
  three_point_circle = circle_points(center = c(0, hoop_center_y), radius = three_point_radius) %>%
    filter(y >= three_point_side_height, y >= hoop_center_y)
  
  three_point_line = data_frame(
    x = c(three_point_side_radius, three_point_side_radius, three_point_circle$x, -three_point_side_radius, -three_point_side_radius),
    y = c(0, three_point_side_height, three_point_circle$y, three_point_side_height, 0),
    desc = "three_point_line"
  )
  
  court_points = bind_rows(
    court_points,
    foul_circle_top,
    foul_circle_bottom,
    hoop,
    restricted,
    three_point_line
  )
  
  
  court_points <- court_points
  
  # Final plot creation
  ggplot() +
    geom_path(
      data = court_points,
      aes(x = x, y = y, group = desc),
      color = court_theme$lines
    ) +
    coord_fixed(ylim = c(0, 45), xlim = c(-25, 25)) +
    theme_minimal(base_size = 22) +
    theme(
      text = element_text(color = court_theme$text),
      plot.background = element_rect(fill = 'gray15', color = 'gray15'),
      panel.background = element_rect(fill = court_theme$court, color = court_theme$court),
      panel.grid = element_blank(),
      panel.border = element_blank(),
      axis.text = element_blank(),
      axis.title = element_blank(),
      axis.ticks = element_blank(),
      legend.background = element_rect(fill = court_theme$court, color = court_theme$court),
      legend.margin = margin(-1, 0, 0, 0, unit = "lines"),
      legend.position = "bottom",
      legend.key = element_blank(),
      legend.text = element_text(size = rel(1.0))
    )
}

```


## Load NBA data

At this point, I'm going to load in data from the 2022 NBA playoffs for the Phoenix Suns. 

```{r}
# 

Sys.setenv("VROOM_CONNECTION_SIZE" = 131072 * 2)

# Grab team names to type into teams_shots function
nba_teams() %>% filter(isNonNBATeam == 0)
# Grab team shot data- Playoffs
team <- teams_shots(teams = "Phoenix Suns", seasons = 2022, season_types = "Playoffs")



# Filter shots by game date
#final_player <- player %>% filter(dateGame == 20210615)

```
## Scrape 2022 Regular Season Data
I'm also going to grab the data for the 2022 regular season. 

```{r}


Sys.setenv("VROOM_CONNECTION_SIZE" = 131072 * 2)

# Grab team names to type into teams_shots function
nba_teams() %>% filter(isNonNBATeam == 0)
# Grab team shot data- Playoffs
team_reg <- teams_shots(teams = "Phoenix Suns", seasons = 2022, season_types = "Regular Season")

```

## Grabbing Chris Paul Data- Playoffs

```{r}

# Filter shot data for player & clean data to fit court dimensions

# Chris Paul- Playoffs
cp3_p <- team %>% filter(namePlayer=="Chris Paul") %>% 
  mutate(x = as.numeric(as.character(locationX)) / 10, y = as.numeric(as.character(locationY)) / 10 + hoop_center_y)
# Horizontally flip the data

 cp3_p$x <- cp3_p$x * -1 
```


## Grabbing Chris Paul Data- Regular Season

```{r}

# Filter shot data for player & clean data to fit court dimensions

# Chris Paul- Regular
cp3_r <- team_reg %>% filter(namePlayer=="Chris Paul") %>% 
  mutate(x = as.numeric(as.character(locationX)) / 10, y = as.numeric(as.character(locationY)) / 10 + hoop_center_y)
# Horizontally flip the data

 cp3_r$x <- cp3_r$x * -1 

```

## Grabbing Devin Booker Data- Playoffs

```{r}

# Filter shot data for player & clean data to fit court dimensions

# Devin Booker- Playoffs
book_p <- team %>% filter(namePlayer=="Devin Booker") %>% 
  mutate(x = as.numeric(as.character(locationX)) / 10, y = as.numeric(as.character(locationY)) / 10 + hoop_center_y)
# Horizontally flip the data

book_p$x <- book_p$x * -1 


```


## Grabbing Devin Booker Data- Regular Season

```{r}

# Filter shot data for player & clean data to fit court dimensions

# Devin Booker- Regular
book_r <- team_reg %>% filter(namePlayer=="Devin Booker") %>% 
  mutate(x = as.numeric(as.character(locationX)) / 10, y = as.numeric(as.character(locationY)) / 10 + hoop_center_y)
# Horizontally flip the data

book_r$x <- book_r$x * -1 

```


## Grabbing Mikal Bridges Data- Playoffs

```{r}


# Filter shot data for player & clean data to fit court dimensions

# Mikal bridges- Playoffs
bridges_p <- team %>% filter(namePlayer=="Mikal Bridges") %>% 
  mutate(x = as.numeric(as.character(locationX)) / 10, y = as.numeric(as.character(locationY)) / 10 + hoop_center_y)
# Horizontally flip the data

bridges_p$x <- bridges_p$x * -1 

```

## Grabbing Mikal Bridges Data- Regular Season

```{r}

# Filter shot data for player & clean data to fit court dimensions

# Mikal bridges- Regular
bridges_r <- team_reg %>% filter(namePlayer=="Mikal Bridges") %>% 
  mutate(x = as.numeric(as.character(locationX)) / 10, y = as.numeric(as.character(locationY)) / 10 + hoop_center_y)
# Horizontally flip the data

bridges_r$x <- bridges_r$x * -1 

```


## Grabbing DeAndre Ayton Data- Playoffs

```{r}

# Filter shot data for player & clean data to fit court dimensions

# DeAndre Ayton- Playoffs
ayton_p <- team %>% filter(namePlayer=="Deandre Ayton") %>% 
  mutate(x = as.numeric(as.character(locationX)) / 10, y = as.numeric(as.character(locationY)) / 10 + hoop_center_y)
# Horizontally flip the data

ayton_p$x <- ayton_p$x * -1 

```

## Grabbing Deandre Ayton Datat- Regular Season

```{r}

# Filter shot data for player & clean data to fit court dimensions

# Deandre Ayton- Regular
ayton_r <- team_reg %>% filter(namePlayer=="Deandre Ayton") %>% 
  mutate(x = as.numeric(as.character(locationX)) / 10, y = as.numeric(as.character(locationY)) / 10 + hoop_center_y)

# Horizontally flip the data

ayton_r$x <- ayton_r$x * -1 

```


## Grabbing Jae Crowder Data- Playoffs

```{r}

# Filter shot data for player & clean data to fit court dimensions

# jae Crowder- Playoffs
crowder_p <- team %>% filter(namePlayer=="Jae Crowder") %>% 
  mutate(x = as.numeric(as.character(locationX)) / 10, y = as.numeric(as.character(locationY)) / 10 + hoop_center_y)
# Horizontally flip the data

crowder_p$x <- crowder_p$x * -1 

```


## Grabbing Jae Crowder Data- Regular Season

```{r}


# Filter shot data for player & clean data to fit court dimensions

# Jae Crowder- Regular
crowder_r <- team_reg %>% filter(namePlayer=="Jae Crowder") %>% 
  mutate(x = as.numeric(as.character(locationX)) / 10, y = as.numeric(as.character(locationY)) / 10 + hoop_center_y)

# Horizontally flip the data

crowder_r$x <- crowder_r$x * -1 


```

## Grabbing Cam Johnson Data- Playoffs

```{r}

# Filter shot data for player & clean data to fit court dimensions

#  Cam Johnson- Playoffs
cam_p <- team %>% filter(namePlayer=="Cameron Johnson") %>% 
  mutate(x = as.numeric(as.character(locationX)) / 10, y = as.numeric(as.character(locationY)) / 10 + hoop_center_y)
# Horizontally flip the data

cam_p$x <- cam_p$x * -1 

```

## Grabbing Cam Johnson Data- Regular Season

```{r}

# Filter shot data for player & clean data to fit court dimensions

# Cam Johnson- Regular
cam_r <- team_reg %>% filter(namePlayer=="Cameron Johnson") %>% 
  mutate(x = as.numeric(as.character(locationX)) / 10, y = as.numeric(as.character(locationY)) / 10 + hoop_center_y)

# Horizontally flip the data

cam_r$x <- cam_r$x * -1 

```

## Grabbing Cameron Paynon Data- Playoffs

```{r}

# Filter shot data for player & clean data to fit court dimensions

#  Cam Payne- Playoffs
payne_p <- team %>% filter(namePlayer=="Cameron Payne") %>% 
  mutate(x = as.numeric(as.character(locationX)) / 10, y = as.numeric(as.character(locationY)) / 10 + hoop_center_y)
# Horizontally flip the data

payne_p$x <- payne_p$x * -1 

```


## Grabbing Cameron Payne Data- Regualr Season


```{r}

# Filter shot data for player & clean data to fit court dimensions

# Cam Payne- Regular
payne_r <- team_reg %>% filter(namePlayer=="Cameron Payne") %>% 
  mutate(x = as.numeric(as.character(locationX)) / 10, y = as.numeric(as.character(locationY)) / 10 + hoop_center_y)

# Horizontally flip the data

payne_r$x <- payne_r$x * -1 

```


## Grabbing Frank Kaminsky Data- Playoffs

```{r}

# Filter shot data for player & clean data to fit court dimensions

#  Frank Kaminsky- Playoffs
kaminsky_p <- team %>% filter(namePlayer=="Frank Kaminsky") %>% 
  mutate(x = as.numeric(as.character(locationX)) / 10, y = as.numeric(as.character(locationY)) / 10 + hoop_center_y)
# Horizontally flip the data

kaminsky_p$x <- kaminsky_p$x * -1 

```


## Grabbing Frank Kaminsky Data- Regular Season

```{r}

## Filter shot data for player & clean data to fit court dimensions

# Frank Kaminsky- Regular
kaminsky_r <- team_reg %>% filter(namePlayer=="Frank Kaminsky") %>% 
  mutate(x = as.numeric(as.character(locationX)) / 10, y = as.numeric(as.character(locationY)) / 10 + hoop_center_y)

# Horizontally flip the data

kaminsky_r$x <- kaminsky_r$x * -1 

```


## Grabbing Javale Mcgee Data- Playoffs

```{r}
# Filter shot data for player & clean data to fit court dimensions

#  Javale McGee- Playoffs
mcgee_p <- team %>% filter(namePlayer=="JaVale McGee") %>% 
  mutate(x = as.numeric(as.character(locationX)) / 10, y = as.numeric(as.character(locationY)) / 10 + hoop_center_y)
# Horizontally flip the data

mcgee_p$x <- mcgee_p$x * -1 

```


## Grabbing JaVale McGee Data- Regular Season

```{r}
## Filter shot data for player & clean data to fit court dimensions

# JaVale McGee- Regular
mcgee_r <- team_reg %>% filter(namePlayer=="JaVale McGee") %>% 
  mutate(x = as.numeric(as.character(locationX)) / 10, y = as.numeric(as.character(locationY)) / 10 + hoop_center_y)

# Horizontally flip the data

mcgee_r$x <- mcgee_r$x * -1 


```


## Heatmaps


### CP3 Playoffs
```{r}

palette <- paletteer::paletteer_d("RColorBrewer::RdPu", direction = -1)
cp3_ph <- plot_court(court_themes$ppt) + 
  geom_density_2d_filled(cp3_p, mapping = aes(x=x,y=y,fill = ..level..,), 
                         contour_var = "ndensity", breaks = seq(0.1, 1.0, length.out = 10), alpha = .5)  + 
  scale_fill_manual(values = c(palette), aesthetics = c("fill", "color")) +
  scale_x_continuous(limits = c(-27.5, 27.5)) + 
  scale_y_continuous(limits = c(0, 45)) +
  theme(legend.position = "none",
        plot.title = element_text(hjust = .5, size = 22, family = "Comic Sans MS", face = "bold", vjust = -4),
        plot.subtitle = element_text(hjust = .5, size = 10, family = "Comic Sans MS", face = "bold", vjust = -8),
        legend.title = element_blank(),
        legend.text = element_text(hjust = .5, size = 10, family = "Comic Sans MS", face = "bold", colour = "white"),
        plot.caption = element_text(hjust = .5, size = 6, family = "Comic Sans MS", face = "bold", colour = "lightgrey", vjust = 8)) +
  labs(title = "Chris Paul",
          subtitle = "2021-22 Playoffs
       PTS/G: 17.5 | FG%: .561      
       FGA: 11.9 | MP: 34.5     ",
       caption = "Visual by: Andrew Lujan | Inspiration: @DSamangy") 
paul_p <- ggdraw(cp3_ph) + theme(plot.background = element_rect(fill="gray15", color = NA)) 
#ggsave("CP3_Heatmap.png", height = 6, width = 6, dpi = 300)

```

### CP3 Regular Season

```{r}

palette <- paletteer::paletteer_d("RColorBrewer::RdPu", direction = -1)
cp3_rh <- plot_court(court_themes$ppt) + 
  geom_density_2d_filled(cp3_r, mapping = aes(x=x,y=y,fill = ..level..,), 
                         contour_var = "ndensity", breaks = seq(0.1, 1.0, length.out = 10), alpha = .5)  + 
  scale_fill_manual(values = c(palette), aesthetics = c("fill", "color")) +
  scale_x_continuous(limits = c(-27.5, 27.5)) + 
  scale_y_continuous(limits = c(0, 45)) +
  theme(legend.position = "none",
        plot.title = element_text(hjust = .5, size = 22, family = "Comic Sans MS", face = "bold", vjust = -4),
        plot.subtitle = element_text(hjust = .5, size = 10, family = "Comic Sans MS", face = "bold", vjust = -8),
        legend.title = element_blank(),
        legend.text = element_text(hjust = .5, size = 10, family = "Comic Sans MS", face = "bold", colour = "white"),
        plot.caption = element_text(hjust = .5, size = 6, family = "Comic Sans MS", face = "bold", colour = "lightgrey", vjust = 8)) +
  labs(title = "Chris Paul",
          subtitle = "2021-22 Regular Season
       PTS/G: 14.7 | FG%: .493      
       FGA: 11.3 | MP: 32.9     ",
       caption = "Visual by: Andrew Lujan | Inspiration: @DSamangy") 
paul_r <- ggdraw(cp3_rh) + theme(plot.background = element_rect(fill="gray15", color = NA))

```


```{r}
# Combining Plots

paul_combined <- grid.arrange(paul_r, paul_p, ncol = 2)

ggsave("CP3_Heatmap.png", paul_combined, height = 6, width = 6, dpi = 300)

```

### Booker Playoffs


```{r}

palette <- paletteer::paletteer_d("RColorBrewer::RdPu", direction = -1)
book_ph <- plot_court(court_themes$ppt) + 
  geom_density_2d_filled(book_p, mapping = aes(x=x,y=y,fill = ..level..,), 
                         contour_var = "ndensity", breaks = seq(0.1, 1.0, length.out = 10), alpha = .5)  + 
  scale_fill_manual(values = c(palette), aesthetics = c("fill", "color")) +
  scale_x_continuous(limits = c(-27.5, 27.5)) + 
  scale_y_continuous(limits = c(0, 45)) +
  theme(legend.position = "none",
        plot.title = element_text(hjust = .5, size = 22, family = "Comic Sans MS", face = "bold", vjust = -4),
        plot.subtitle = element_text(hjust = .5, size = 10, family = "Comic Sans MS", face = "bold", vjust = -8),
        legend.title = element_blank(),
        legend.text = element_text(hjust = .5, size = 10, family = "Comic Sans MS", face = "bold", colour = "white"),
        plot.caption = element_text(hjust = .5, size = 6, family = "Comic Sans MS", face = "bold", colour = "lightgrey", vjust = 8)) +
  labs(title = "Devin Booker",
          subtitle = "2021-22 Playoffs
       PTS/G: 23.3 | FG%: .451      
       FGA: 17.5 | MP: 36.6     ",
       caption = "Visual by: Andrew Lujan | Inspiration: @DSamangy") 
booker_p <- ggdraw(book_ph) + theme(plot.background = element_rect(fill="gray15", color = NA)) 

```

## Devin Booker Regular Season

```{r}

palette <- paletteer::paletteer_d("RColorBrewer::RdPu", direction = -1)
book_rh <- plot_court(court_themes$ppt) + 
  geom_density_2d_filled(book_r, mapping = aes(x=x,y=y,fill = ..level..,), 
                         contour_var = "ndensity", breaks = seq(0.1, 1.0, length.out = 10), alpha = .5)  + 
  scale_fill_manual(values = c(palette), aesthetics = c("fill", "color")) +
  scale_x_continuous(limits = c(-27.5, 27.5)) + 
  scale_y_continuous(limits = c(0, 45)) +
  theme(legend.position = "none",
        plot.title = element_text(hjust = .5, size = 22, family = "Comic Sans MS", face = "bold", vjust = -4),
        plot.subtitle = element_text(hjust = .5, size = 10, family = "Comic Sans MS", face = "bold", vjust = -8),
        legend.title = element_blank(),
        legend.text = element_text(hjust = .5, size = 10, family = "Comic Sans MS", face = "bold", colour = "white"),
        plot.caption = element_text(hjust = .5, size = 6, family = "Comic Sans MS", face = "bold", colour = "lightgrey", vjust = 8)) +
  labs(title = "Devin Booker",
          subtitle = "2021-22 Regular Season
       PTS/G: 26.8 | FG%: .466      
       FGA: 20.9 | MP: 34.5     ",
       caption = "Visual by: Andrew Lujan | Inspiration: @DSamangy") 
booker_r <- ggdraw(book_rh) + theme(plot.background = element_rect(fill="gray15", color = NA))

```

## Combine Booker Plots

```{r}

# Combining Plots

booker_combined <- grid.arrange(booker_r, booker_p, ncol = 2)

ggsave("Book_Heatmap.png", booker_combined, height = 6, width = 6, dpi = 300)

```
## Mikal Bridges Playoffs

```{r}

palette <- paletteer::paletteer_d("RColorBrewer::RdPu", direction = -1)
bridges_ph <- plot_court(court_themes$ppt) + 
  geom_density_2d_filled(bridges_p, mapping = aes(x=x,y=y,fill = ..level..,), 
                         contour_var = "ndensity", breaks = seq(0.1, 1.0, length.out = 10), alpha = .5)  + 
  scale_fill_manual(values = c(palette), aesthetics = c("fill", "color")) +
  scale_x_continuous(limits = c(-27.5, 27.5)) + 
  scale_y_continuous(limits = c(0, 45)) +
  theme(legend.position = "none",
        plot.title = element_text(hjust = .5, size = 22, family = "Comic Sans MS", face = "bold", vjust = -4),
        plot.subtitle = element_text(hjust = .5, size = 10, family = "Comic Sans MS", face = "bold", vjust = -8),
        legend.title = element_blank(),
        legend.text = element_text(hjust = .5, size = 10, family = "Comic Sans MS", face = "bold", colour = "white"),
        plot.caption = element_text(hjust = .5, size = 6, family = "Comic Sans MS", face = "bold", colour = "lightgrey", vjust = 8)) +
  labs(title = "Mikal Bridges",
          subtitle = "2021-22 Playoffs
       PTS/G: 13.3 | FG%: .478      
       FGA: 10.6 | MP: 38.5     ",
       caption = "Visual by: Andrew Lujan | Inspiration: @DSamangy") 
bridges_play <- ggdraw(bridges_ph) + theme(plot.background = element_rect(fill="gray15", color = NA)) 

```

## Mikal Bridges Regular Season

```{r}

palette <- paletteer::paletteer_d("RColorBrewer::RdPu", direction = -1)
bridges_rh <- plot_court(court_themes$ppt) + 
  geom_density_2d_filled(bridges_r, mapping = aes(x=x,y=y,fill = ..level..,), 
                         contour_var = "ndensity", breaks = seq(0.1, 1.0, length.out = 10), alpha = .5)  + 
  scale_fill_manual(values = c(palette), aesthetics = c("fill", "color")) +
  scale_x_continuous(limits = c(-27.5, 27.5)) + 
  scale_y_continuous(limits = c(0, 45)) +
  theme(legend.position = "none",
        plot.title = element_text(hjust = .5, size = 22, family = "Comic Sans MS", face = "bold", vjust = -4),
        plot.subtitle = element_text(hjust = .5, size = 10, family = "Comic Sans MS", face = "bold", vjust = -8),
        legend.title = element_blank(),
        legend.text = element_text(hjust = .5, size = 10, family = "Comic Sans MS", face = "bold", colour = "white"),
        plot.caption = element_text(hjust = .5, size = 6, family = "Comic Sans MS", face = "bold", colour = "lightgrey", vjust = 8)) +
  labs(title = "Mikal Bridges",
          subtitle = "2021-22 Regular Season
       PTS/G: 14.2 | FG%: .534      
       FGA: 10.5 | MP: 34.8     ",
       caption = "Visual by: Andrew Lujan | Inspiration: @DSamangy") 
bridges_reg <- ggdraw(bridges_rh) + theme(plot.background = element_rect(fill="gray15", color = NA))

```

## Mikal Bridges Combined Heatmap

```{r}

# Combining Plots

bridges_combined <- grid.arrange(bridges_reg, bridges_play, ncol = 2)

ggsave("Bridges_Heatmap.png", booker_combined, height = 6, width = 6, dpi = 300)

```

## Deandre Ayton Playoffs Heatmap

```{r}

palette <- paletteer::paletteer_d("RColorBrewer::RdPu", direction = -1)
ayton_ph <- plot_court(court_themes$ppt) + 
  geom_density_2d_filled(ayton_p, mapping = aes(x=x,y=y,fill = ..level..,), 
                         contour_var = "ndensity", breaks = seq(0.1, 1.0, length.out = 10), alpha = .5)  + 
  scale_fill_manual(values = c(palette), aesthetics = c("fill", "color")) +
  scale_x_continuous(limits = c(-27.5, 27.5)) + 
  scale_y_continuous(limits = c(0, 45)) +
  theme(legend.position = "none",
        plot.title = element_text(hjust = .5, size = 22, family = "Comic Sans MS", face = "bold", vjust = -4),
        plot.subtitle = element_text(hjust = .5, size = 10, family = "Comic Sans MS", face = "bold", vjust = -8),
        legend.title = element_blank(),
        legend.text = element_text(hjust = .5, size = 10, family = "Comic Sans MS", face = "bold", colour = "white"),
        plot.caption = element_text(hjust = .5, size = 6, family = "Comic Sans MS", face = "bold", colour = "lightgrey", vjust = 8)) +
  labs(title = "Deandre Ayton",
          subtitle = "2021-22 Playoffs
       PTS/G: 17.9 | FG%: .640      
       FGA: 12.6 | MP: 30.5     ",
       caption = "Visual by: Andrew Lujan | Inspiration: @DSamangy") 
ayton_play <- ggdraw(ayton_ph) + theme(plot.background = element_rect(fill="gray15", color = NA)) 

```

## Deandre Ayton Regular Season Heatmap

```{r}

palette <- paletteer::paletteer_d("RColorBrewer::RdPu", direction = -1)
ayton_rh <- plot_court(court_themes$ppt) + 
  geom_density_2d_filled(ayton_r, mapping = aes(x=x,y=y,fill = ..level..,), 
                         contour_var = "ndensity", breaks = seq(0.1, 1.0, length.out = 10), alpha = .5)  + 
  scale_fill_manual(values = c(palette), aesthetics = c("fill", "color")) +
  scale_x_continuous(limits = c(-27.5, 27.5)) + 
  scale_y_continuous(limits = c(0, 45)) +
  theme(legend.position = "none",
        plot.title = element_text(hjust = .5, size = 22, family = "Comic Sans MS", face = "bold", vjust = -4),
        plot.subtitle = element_text(hjust = .5, size = 10, family = "Comic Sans MS", face = "bold", vjust = -8),
        legend.title = element_blank(),
        legend.text = element_text(hjust = .5, size = 10, family = "Comic Sans MS", face = "bold", colour = "white"),
        plot.caption = element_text(hjust = .5, size = 6, family = "Comic Sans MS", face = "bold", colour = "lightgrey", vjust = 8)) +
  labs(title = "Deandre Ayton",
          subtitle = "2021-22 Regular Season
       PTS/G: 17.2 | FG%: .634      
       FGA: 12.0 | MP: 29.5     ",
       caption = "Visual by: Andrew Lujan | Inspiration: @DSamangy") 
ayton_reg <- ggdraw(ayton_rh) + theme(plot.background = element_rect(fill="gray15", color = NA))

```

## Deandre Ayton Combined Heatmap

```{r}

# Combining Plots

ayton_combined <- grid.arrange(ayton_reg, ayton_play, ncol = 2)

ggsave("Ayton_Heatmap.png", ayton_combined, height = 6, width = 6, dpi = 300)

```

## Jae Crowder Playoff Heatmap

```{r}

palette <- paletteer::paletteer_d("RColorBrewer::RdPu", direction = -1)
crowder_ph <- plot_court(court_themes$ppt) + 
  geom_density_2d_filled(crowder_p, mapping = aes(x=x,y=y,fill = ..level..,), 
                         contour_var = "ndensity", breaks = seq(0.1, 1.0, length.out = 10), alpha = .5)  + 
  scale_fill_manual(values = c(palette), aesthetics = c("fill", "color")) +
  scale_x_continuous(limits = c(-27.5, 27.5)) + 
  scale_y_continuous(limits = c(0, 45)) +
  theme(legend.position = "none",
        plot.title = element_text(hjust = .5, size = 22, family = "Comic Sans MS", face = "bold", vjust = -4),
        plot.subtitle = element_text(hjust = .5, size = 10, family = "Comic Sans MS", face = "bold", vjust = -8),
        legend.title = element_blank(),
        legend.text = element_text(hjust = .5, size = 10, family = "Comic Sans MS", face = "bold", colour = "white"),
        plot.caption = element_text(hjust = .5, size = 6, family = "Comic Sans MS", face = "bold", colour = "lightgrey", vjust = 8)) +
  labs(title = "Jae Crowder",
          subtitle = "2021-22 Playoffs
       PTS/G: 9.4 | FG%: .400      
       FGA: 8.1 | MP: 29.5     ",
       caption = "Visual by: Andrew Lujan | Inspiration: @DSamangy") 
crowder_play <- ggdraw(crowder_ph) + theme(plot.background = element_rect(fill="gray15", color = NA)) 

```

## Jae Crowder Regular Season Heatmap

```{r}

palette <- paletteer::paletteer_d("RColorBrewer::RdPu", direction = -1)
crowder_rh <- plot_court(court_themes$ppt) + 
  geom_density_2d_filled(crowder_r, mapping = aes(x=x,y=y,fill = ..level..,), 
                         contour_var = "ndensity", breaks = seq(0.1, 1.0, length.out = 10), alpha = .5)  + 
  scale_fill_manual(values = c(palette), aesthetics = c("fill", "color")) +
  scale_x_continuous(limits = c(-27.5, 27.5)) + 
  scale_y_continuous(limits = c(0, 45)) +
  theme(legend.position = "none",
        plot.title = element_text(hjust = .5, size = 22, family = "Comic Sans MS", face = "bold", vjust = -4),
        plot.subtitle = element_text(hjust = .5, size = 10, family = "Comic Sans MS", face = "bold", vjust = -8),
        legend.title = element_blank(),
        legend.text = element_text(hjust = .5, size = 10, family = "Comic Sans MS", face = "bold", colour = "white"),
        plot.caption = element_text(hjust = .5, size = 6, family = "Comic Sans MS", face = "bold", colour = "lightgrey", vjust = 8)) +
  labs(title = "Jae Crowder",
          subtitle = "2021-22 Regular Season
       PTS/G: 9.4 | FG%: .399      
       FGA: 8.1 | MP: 28.1     ",
       caption = "Visual by: Andrew Lujan | Inspiration: @DSamangy") 
crowder_reg <- ggdraw(crowder_rh) + theme(plot.background = element_rect(fill="gray15", color = NA))

```

## Jae Crowder Combined Heatmap

```{r}

# Combining Plots

crowder_combined <- grid.arrange(crowder_reg, crowder_play, ncol = 2)

ggsave("Crowder_Heatmap.png", crowder_combined, height = 6, width = 6, dpi = 300)

```

## Cam Johnson Playoff Heatmap

```{r}

palette <- paletteer::paletteer_d("RColorBrewer::RdPu", direction = -1)
cam_ph <- plot_court(court_themes$ppt) + 
  geom_density_2d_filled(cam_p, mapping = aes(x=x,y=y,fill = ..level..,), 
                         contour_var = "ndensity", breaks = seq(0.1, 1.0, length.out = 10), alpha = .5)  + 
  scale_fill_manual(values = c(palette), aesthetics = c("fill", "color")) +
  scale_x_continuous(limits = c(-27.5, 27.5)) + 
  scale_y_continuous(limits = c(0, 45)) +
  theme(legend.position = "none",
        plot.title = element_text(hjust = .5, size = 22, family = "Comic Sans MS", face = "bold", vjust = -4),
        plot.subtitle = element_text(hjust = .5, size = 10, family = "Comic Sans MS", face = "bold", vjust = -8),
        legend.title = element_blank(),
        legend.text = element_text(hjust = .5, size = 10, family = "Comic Sans MS", face = "bold", colour = "white"),
        plot.caption = element_text(hjust = .5, size = 6, family = "Comic Sans MS", face = "bold", colour = "lightgrey", vjust = 8)) +
  labs(title = "Cam Johnson",
          subtitle = "2021-22 Playoffs
       PTS/G: 10.8 | FG%: .465      
       FGA: 7.6 | MP: 24.6     ",
       caption = "Visual by: Andrew Lujan | Inspiration: @DSamangy") 
cam_play <- ggdraw(cam_ph) + theme(plot.background = element_rect(fill="gray15", color = NA)) 

```

## Cam Johnson Regular Season Heatmap

```{r}

palette <- paletteer::paletteer_d("RColorBrewer::RdPu", direction = -1)
cam_rh <- plot_court(court_themes$ppt) + 
  geom_density_2d_filled(cam_r, mapping = aes(x=x,y=y,fill = ..level..,), 
                         contour_var = "ndensity", breaks = seq(0.1, 1.0, length.out = 10), alpha = .5)  + 
  scale_fill_manual(values = c(palette), aesthetics = c("fill", "color")) +
  scale_x_continuous(limits = c(-27.5, 27.5)) + 
  scale_y_continuous(limits = c(0, 45)) +
  theme(legend.position = "none",
        plot.title = element_text(hjust = .5, size = 22, family = "Comic Sans MS", face = "bold", vjust = -4),
        plot.subtitle = element_text(hjust = .5, size = 10, family = "Comic Sans MS", face = "bold", vjust = -8),
        legend.title = element_blank(),
        legend.text = element_text(hjust = .5, size = 10, family = "Comic Sans MS", face = "bold", colour = "white"),
        plot.caption = element_text(hjust = .5, size = 6, family = "Comic Sans MS", face = "bold", colour = "lightgrey", vjust = 8)) +
  labs(title = "Cam Johnson",
          subtitle = "2021-22 Regular Season
       PTS/G: 12.5 | FG%: .460      
       FGA: 9.2 | MP: 26.2     ",
       caption = "Visual by: Andrew Lujan | Inspiration: @DSamangy") 
cam_reg <- ggdraw(cam_rh) + theme(plot.background = element_rect(fill="gray15", color = NA))

```

## Cam Johnson Combined Heatmap

```{r}

# Combining Plots

cam_combined <- grid.arrange(cam_reg, cam_play, ncol = 2)

ggsave("Cam_Heatmap.png", cam_combined, height = 6, width = 6, dpi = 300)

```


## Cameron Payne Playoff Heatmap

```{r}

palette <- paletteer::paletteer_d("RColorBrewer::RdPu", direction = -1)
payne_ph <- plot_court(court_themes$ppt) + 
  geom_density_2d_filled(payne_p, mapping = aes(x=x,y=y,fill = ..level..,), 
                         contour_var = "ndensity", breaks = seq(0.1, 1.0, length.out = 10), alpha = .5)  + 
  scale_fill_manual(values = c(palette), aesthetics = c("fill", "color")) +
  scale_x_continuous(limits = c(-27.5, 27.5)) + 
  scale_y_continuous(limits = c(0, 45)) +
  theme(legend.position = "none",
        plot.title = element_text(hjust = .5, size = 22, family = "Comic Sans MS", face = "bold", vjust = -4),
        plot.subtitle = element_text(hjust = .5, size = 10, family = "Comic Sans MS", face = "bold", vjust = -8),
        legend.title = element_blank(),
        legend.text = element_text(hjust = .5, size = 10, family = "Comic Sans MS", face = "bold", colour = "white"),
        plot.caption = element_text(hjust = .5, size = 6, family = "Comic Sans MS", face = "bold", colour = "lightgrey", vjust = 8)) +
  labs(title = "Cameron Payne",
          subtitle = "2021-22 Playoffs
       PTS/G: 4.2 | FG%: .297      
       FGA: 5.7 | MP: 13.2     ",
       caption = "Visual by: Andrew Lujan | Inspiration: @DSamangy") 
payne_play <- ggdraw(payne_ph) + theme(plot.background = element_rect(fill="gray15", color = NA)) 

```

## Cameron Payne Regular Season Heatmap

```{r}

palette <- paletteer::paletteer_d("RColorBrewer::RdPu", direction = -1)
payne_rh <- plot_court(court_themes$ppt) + 
  geom_density_2d_filled(payne_r, mapping = aes(x=x,y=y,fill = ..level..,), 
                         contour_var = "ndensity", breaks = seq(0.1, 1.0, length.out = 10), alpha = .5)  + 
  scale_fill_manual(values = c(palette), aesthetics = c("fill", "color")) +
  scale_x_continuous(limits = c(-27.5, 27.5)) + 
  scale_y_continuous(limits = c(0, 45)) +
  theme(legend.position = "none",
        plot.title = element_text(hjust = .5, size = 22, family = "Comic Sans MS", face = "bold", vjust = -4),
        plot.subtitle = element_text(hjust = .5, size = 10, family = "Comic Sans MS", face = "bold", vjust = -8),
        legend.title = element_blank(),
        legend.text = element_text(hjust = .5, size = 10, family = "Comic Sans MS", face = "bold", colour = "white"),
        plot.caption = element_text(hjust = .5, size = 6, family = "Comic Sans MS", face = "bold", colour = "lightgrey", vjust = 8)) +
  labs(title = "Cameron Payne",
          subtitle = "2021-22 Regular Season
       PTS/G: 10.8 | FG%: .409      
       FGA: 10.1 | MP: 22.0     ",
       caption = "Visual by: Andrew Lujan | Inspiration: @DSamangy") 
payne_reg <- ggdraw(payne_rh) + theme(plot.background = element_rect(fill="gray15", color = NA))

```

## Cameron Payne combined heatmaps

```{r}

# Combining Plots

payne_combined <- grid.arrange(payne_reg, payne_play, ncol = 2)

ggsave("Payne_Heatmap.png", payne_combined, height = 6, width = 6, dpi = 300)

```

## Javale McGee Playoff heatmaps

```{r}

palette <- paletteer::paletteer_d("RColorBrewer::RdPu", direction = -1)
mcgee_ph <- plot_court(court_themes$ppt) + 
  geom_density_2d_filled(mcgee_p, mapping = aes(x=x,y=y,fill = ..level..,), 
                         contour_var = "ndensity", breaks = seq(0.1, 1.0, length.out = 10), alpha = .5)  + 
  scale_fill_manual(values = c(palette), aesthetics = c("fill", "color")) +
  scale_x_continuous(limits = c(-27.5, 27.5)) + 
  scale_y_continuous(limits = c(0, 45)) +
  theme(legend.position = "none",
        plot.title = element_text(hjust = .5, size = 22, family = "Comic Sans MS", face = "bold", vjust = -4),
        plot.subtitle = element_text(hjust = .5, size = 10, family = "Comic Sans MS", face = "bold", vjust = -8),
        legend.title = element_blank(),
        legend.text = element_text(hjust = .5, size = 10, family = "Comic Sans MS", face = "bold", colour = "white"),
        plot.caption = element_text(hjust = .5, size = 6, family = "Comic Sans MS", face = "bold", colour = "lightgrey", vjust = 8)) +
  labs(title = "JaVale McGee",
          subtitle = "2021-22 Playoffs
       PTS/G: 6.8 | FG%: .700      
       FGA: 4.2 | MP: 11.1     ",
       caption = "Visual by: Andrew Lujan | Inspiration: @DSamangy") 
mcgee_play <- ggdraw(mcgee_ph) + theme(plot.background = element_rect(fill="gray15", color = NA))

```

## JaVale McGee Regular Season Heatmaps

```{r}

palette <- paletteer::paletteer_d("RColorBrewer::RdPu", direction = -1)
mcgee_rh <- plot_court(court_themes$ppt) + 
  geom_density_2d_filled(mcgee_r, mapping = aes(x=x,y=y,fill = ..level..,), 
                         contour_var = "ndensity", breaks = seq(0.1, 1.0, length.out = 10), alpha = .5)  + 
  scale_fill_manual(values = c(palette), aesthetics = c("fill", "color")) +
  scale_x_continuous(limits = c(-27.5, 27.5)) + 
  scale_y_continuous(limits = c(0, 45)) +
  theme(legend.position = "none",
        plot.title = element_text(hjust = .5, size = 22, family = "Comic Sans MS", face = "bold", vjust = -4),
        plot.subtitle = element_text(hjust = .5, size = 10, family = "Comic Sans MS", face = "bold", vjust = -8),
        legend.title = element_blank(),
        legend.text = element_text(hjust = .5, size = 10, family = "Comic Sans MS", face = "bold", colour = "white"),
        plot.caption = element_text(hjust = .5, size = 6, family = "Comic Sans MS", face = "bold", colour = "lightgrey", vjust = 8)) +
  labs(title = "JaVale McGee",
          subtitle = "2021-22 Regular Season
       PTS/G: 9.2 | FG%: .629      
       FGA: 6.2 | MP: 15.8     ",
       caption = "Visual by: Andrew Lujan | Inspiration: @DSamangy") 
mcgee_reg <- ggdraw(mcgee_rh) + theme(plot.background = element_rect(fill="gray15", color = NA))


```


## JaVale McGee combined heatmaps

```{r}

# Combining Plots

mcgee_combined <- grid.arrange(mcgee_reg, mcgee_play, ncol = 2)

ggsave("McGee_Heatmap.png", mcgee_combined, height = 6, width = 6, dpi = 300)

```

